### 2018-06-01 CS761-RandomizedAlgorithms/assignments/a1.tex
5ab5ab5ab5ab5ab

>>>>

\newpage
\section{}
\subsection{a}
\paragraph{}
\begin{align*}
M_{X^2}(t) &= E[e^{tX^2}] \\
&= \int_{-\infty}^\infty e^{tx^2}f(x)dx \\
&=\int_{-\infty}^\infty \frac{1}{\sqrt{2\pi}}e^{tx^2-\frac{1}{2}x^2}dx \\
&= \int_{-\infty}^\infty \frac{1}{\sqrt{2\pi}}e^{\frac{-1}{2}(1-2t)x^2}dx \\
&= \frac{1}{\sqrt{1-2t}}\int_{-\infty}^\infty \frac{1}{\sqrt{2\pi}}e^{z^2}dz &\text{Taking $z=\sqrt{1-2t}x$} \\
&= \frac{1}{\sqrt{1-2t}} &\text{Using $\int_{-\infty}^\infty f(x)dx = 1$}.
\end{align*}
\subsection{b}
\paragraph{}
Using Taylor expansion we have
\begin{align*}
E[X^4] = M_{X^2}^{(2)}(0).
\end{align*}
Now observe that
$$M_{X^2}^{(2)}(t) = \frac{3}{(1-2t)^{5/2}}$$
and so
$$M_{X^2}^{(2)}(0) = 3.$$
Therefore $E[X^4] = 3$.
\subsection{c}
